Analysis for Non-Expressive performances (ONSET)

### 2020-04-16 material/analysis/expression/stim_a/ioi_onset.Rmd
remove performances containing NA
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

```{r extract, include = FALSE}
dt_ioi_original <- fread("../trimmed/data_ioi_1.csv", header = T, sep = ",", dec = ".") # read a filtered csv
# Include only articulation
dt_ioi <- dt_ioi_original[Condition == "performing" & Skill == "articulation"]

# SubNr as a factor
dt_ioi$SubNr <- as.factor(dt_ioi$SubNr)
dt_ioi$TrialNr <- as.factor(dt_ioi$TrialNr)
```

@@

```{r ioi, echo = FALSE}
# For each individual
ioi <- dt_ioi[, .(N = length(normIOI), Mean = mean(normIOI), SD = sd(normIOI)), by = .(SubNr)]
print(ioi)
```

@@

```{r ioi_seq, fig.width = 14, fig.height = 20, echo = FALSE}
# For each individual
ioi_seq <- dt_ioi[, .(N = length(normIOI), Mean = mean(normIOI)), by = .(SubNr, TrialNr, Interval)]

@@

```{r ioi_dis, fig.width = 14, fig.height = 8, echo = FALSE}
p_ioi_dis <- ggplot(dt_ioi, aes(x = normIOI)) +
  geom_histogram(binwidth = .02, alpha = .5, position = "identity") +
  facet_grid(TrialNr ~ SubNr) +
  labs(x = "Normalised IOI", y = "Count", subtitle = "IOI: Performing-Articulation")
p_ioi_dis
```

@@

```{r cv_box, echo = FALSE}
p_cv_box <- ggplot(cv, aes(x = SubNr, y = CV)) +
  geom_boxplot() +
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.3)
p_cv_box
```

>>>>

```{r extract, include = FALSE}
dt_onset <- fread("../filtered/data_correct_onset.csv", header = T, sep = ",", dec = ".") # read a filtered csv
dt_error <- fread("../filtered/data_error_correction_onset.csv", header = T, sep = ",", dec = ".") # read an error csv
# assign RowNr
dt_onset$RowNr <- rep(1:72, nrow(dt_onset)/72)
# sort by SubNr, BlockNr, TrialNr and NoteNr
dt_onset <- dt_onset[order(SubNr, BlockNr, TrialNr, RowNr),]
# include only articulation
dt_ioi <- dt_onset[Condition == "performing" & Skill == "articulation"]

# SubNr as a factor
dt_ioi$SubNr <- as.factor(dt_ioi$SubNr)
dt_ioi$TrialNr <- as.factor(dt_ioi$TrialNr)

# remove performances which contain NA
dt_ioi$Error <- 0
for (error in 1:nrow(dt_error)){
  dt_ioi[SubNr == dt_error[error]$SubNr & BlockNr == dt_error[error]$BlockNr & TrialNr == dt_error[error]$TrialNr]$Error <- 1
}
dt_ioi_ori <- dt_ioi # save original data
dt_ioi <- dt_ioi_ori[Error == 0]
```

```{r normIOIs, include = FALSE}
# calculate normIOIs
dt_ioi$IOI <- diff(c(0, dt_ioi$TimeStamp))

# convert bpm to ms
dt_ioi[Tempo == 120]$Tempo <- 250
dt_ioi[Tempo == 110]$Tempo <- 273
dt_ioi[Tempo == 100]$Tempo <- 300

# normalise IOIs
dt_ioi$normIOI <- dt_ioi$IOI/dt_ioi$Tempo

# remove the first note
dt_ioi <- dt_ioi[RowNr != 1]

# assign Interval
dt_ioi$Interval <- rep(1:71, nrow(dt_ioi)/71)

# remove irrelevant intervals
ls_irrelevant <- list(c(25:28), c(32:35), c(51:52), c(56:57), c(65:71))
dt_ioi$EighthNote <- "Yes"

for (phrase in 1:length(ls_irrelevant)){
  for (note in 1:length(ls_irrelevant[[phrase]])){
    dt_ioi[Interval == ls_irrelevant[[phrase]][note]]$EighthNote <- "No"
  }
}
```

@@

```{r ioi, echo = FALSE}
# For each individual
ioi <- dt_ioi[EighthNote == "Yes", .(N = length(normIOI), Mean = mean(normIOI), SD = sd(normIOI)), by = .(SubNr)]
print(ioi)
```

@@

```{r ioi_seq, fig.width = 14, fig.height = 20, echo = FALSE}
# For each individual
ioi_seq <- dt_ioi[EighthNote == "Yes", .(N = length(normIOI), Mean = mean(normIOI)), by = .(SubNr, TrialNr, Interval)]

@@

```{r ioi_dis, fig.width = 14, fig.height = 8, echo = FALSE}
p_ioi_dis <- ggplot(dt_ioi[EighthNote == "Yes"], aes(x = normIOI)) +
  geom_histogram(binwidth = .05, alpha = .5, position = "identity") +
  facet_grid(TrialNr ~ SubNr) +
  labs(x = "Normalised IOI", y = "Count", subtitle = "IOI: Performing-Articulation")
p_ioi_dis
```

@@

```{r cv_box, echo = FALSE}
p_cv_box <- ggplot(cv, aes(x = SubNr, y = CV)) +
  geom_boxplot() +
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.5)
p_cv_box
```
